---
title: "Hello"
format:
  html:
    theme: default
    toc: true
    toc-location: right
execute:
  echo: false
  warnings: false
  message: false
sidebar: false
params:
  data: "jct"
  jns: NULL
---

```{r setup, message=FALSE}
library(tidyverse)
library(ggiraph)
library(patchwork)
```


How open are transformative agreements? This dashboard highlights the Open Access uptake in hybrid journals as listed by the cOAlitionS Journal Checker Tool over time by open license, publisher and country. You can also monitor the availability of publisher-provided metadata in Crossref

```{r jct_jn_data, message = FALSE}
#| eval: !expr params$data == "jct"

jct_hybrid_jns <- readr::read_csv("data/jct_hybrid_jns.csv")
if(!is.null(params$jns))
jct_hybrid_jns <-
  jct_hybrid_jns |>
    filter(issn_l %in% params$jns)

cc_openalex_inst_jn_ind <- readr::read_csv("data/cc_openalex_inst_jn_ind.csv") |>
  rename(jn_id = issn_l) |> 
  dplyr::filter(jn_id %in% jct_hybrid_jns$issn_l) |>
  dplyr::mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    )))
  
cc_jn_ind <- readr::read_csv("data/cc_jn_ind.csv") |>
  rename(jn_id = issn_l) |>
  dplyr::filter(jn_id %in% jct_hybrid_jns$issn_l) |>
  mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    )))
```

```{r oam_data, message = FALSE}
#| eval: !expr params$data == "oam"

library(hoaddata)
if(!is.null(params$jns)) 
  oam_hybrid_jns <- oam_hybrid_jns |>
    dplyr::filter(cr_journal_id %in% params$jns)

cc_openalex_inst_jn_ind <- cc_openalex_inst_jn_ind |>
  rename(jn_id = cr_journal_id) |>
  dplyr::filter(jn_id %in% oam_hybrid_jns$cr_journal_id)

 cc_jn_ind <- cc_jn_ind |>
  rename(jn_id = cr_journal_id) |>
  dplyr::filter(jn_id %in% oam_hybrid_jns$cr_journal_id)
```

The share of Open Access articles with a Creative Commons license in hybrid journals is as follows:

{{< include _teaser.qmd >}}

::: {.callout-note collapse="true"}
## Expand to learn about how publications from Germany were counted?

Only journal articles from lead authors based in Germany were considered. A [lead author](https://en.wikipedia.org/wiki/Lead_author) is the first named author of a scholarly article who has usually undertaken most of the research presented in the article, although author roles can vary across discipline. We used [OpenAlex](https://openalex.org/) as data source to determine lead author affiliation.
:::

## Open Licensing

Open access articles in hybrid journals are usually published under an Creative Commons license, preferably the Creative Commons Attribution licence (CC BY). The [ESAC guidelines](https://esac-initiative.org/about/transformative-agreements/guidelines-for-transformative-agreements/) and an increasing number of transformative agreements request that publishers register Creative Commons licensing information in their Crossref metadata. The following charts draw on this information to showcase the percentage of Creative Commons licensed open access articles over time by license type and publisher.

### Creative Commons licenses over time

Percentage of Open Access in hybrid journals included in transformative agreements by Creative Commons license types as provided by Crossref.

{{< include _cc_over_year.qmd >}}

### Creative Commons licenses over time by publisher

Percentage of Open Access in hybrid journals included in transformative agreements by Creative Commons license types and Top 13 publishers in terms of total articles published between 2017 and 2022.

```{r}
cc_jn_ind_pub <- jct_hybrid_jns |>
  select(jn_id = issn_l, esac_publisher) |>
  inner_join(cc_jn_ind, by = "jn_id") |>
  distinct()

all_df <- cc_jn_ind_pub |>
  distinct(cr_year, esac_publisher, jn_id, jn_all) |>
  group_by(cr_year, esac_publisher) |>
  summarise(
    journals = n_distinct(jn_id),
    all_articles = sum(jn_all))

top_cc_publisher <- cc_jn_ind_pub |>
  filter(!is.na(cc)) |>
  group_by(esac_publisher) |>
  summarise(cc_total = sum(cc_total)) |>
  arrange(desc(cc_total)) |>
  pull(esac_publisher)

top_publisher <- 
  all_df |>
  group_by(esac_publisher) |>
  summarise(n = sum(all_articles))  |>
  arrange(desc(n)) |>
  pull(esac_publisher)

top <- top_publisher[1:13]

all_top <- cc_jn_ind_pub |>
   ungroup() |>
  right_join(all_df, by = c("esac_publisher", "cr_year")) |>
  mutate(publisher_fct = forcats::fct_other(esac_publisher, keep = top)) |>
  mutate(publisher_fct = forcats::fct_relevel(publisher_fct, top, "Other")) |>
  distinct(cr_year, publisher_fct, jn_id, jn_all) |>
  group_by(cr_year, publisher_fct) |>
  summarise(
    journals = n_distinct(jn_id),
    all_articles = sum(jn_all))


cc_top <- cc_jn_ind_pub |>
    ungroup() |>
  filter(!is.na(cc)) |>
  mutate(publisher_fct = forcats::fct_other(esac_publisher, keep = top)) |>
  mutate(publisher_fct = forcats::fct_relevel(publisher_fct, top, "Other")) |>
  group_by(cr_year, publisher_fct, cc) |>
  summarise(cc_total = sum(cc_total)) |>
  inner_join(all_top, by = c("publisher_fct", "cr_year")) |>
  mutate(prop = cc_total / all_articles) |>
  ungroup() |>
  tidyr::complete(cc, nesting(cr_year, publisher_fct), fill = list(cc_total = 0, prop = 0))

## Plot config

### Tooltips

total_by_year <- cc_top |>
  group_by(cr_year, publisher_fct) |>
  summarise(cc_total_all = sum(cc_total),
              cc_total_prop = sum(prop))
  
 my_tooltips <-
   cc_top |>
   filter(!is.na(cc)) |>
    mutate(colors = case_when(
        cc == "CC BY" ~ "#65BADA",
        cc == "CC BY-SA" ~ "#068E8C",
        cc == "CC BY-NC" ~ "#00A757",
        cc == "CC BY-NC-SA" ~ "#E5BA52",
        cc == "CC BY-ND" ~ "#D86F27",
        cc == "CC BY-NC-ND" ~ "#C82E6B")) |>
      mutate(tooltip = glue::glue('
<tr>
    <td style="text-align:left;padding-bottom:0"><span style="color:{colors}">■</span> {cc}<br></td>
    <td style="text-align:right;padding-bottom:0">{format(cc_total, big.mark = ",")}</td>
    <td style="text-align:right;">{round(prop * 100, 1)}%</td>
</tr>')) |>
      group_by(cr_year, publisher_fct) |>
      summarise(tooltip_group = paste(tooltip, collapse = "")) |>
      inner_join(total_by_year, by = c("cr_year", "publisher_fct")) |>
      mutate(tooltip_group = glue::glue('<h3><span class="text-muted">Articles with Creative Commons license<br></span>in <b>{cr_year}</h3><hr><table style="margin:8px 0 0;padding:0;width:100%">
  <colgroup>
       <col span="1" style="width: 50%;">
       <col span="1" style="width: 30%;">
       <col span="1" style="width: 20%;">
      </colgroup>
    <tbody>
    {tooltip_group}
 <tr style="padding-top:5px">
    <td style="text-align:left;padding-bottom:0;font-weight:bold;"><span style="color:transparent">■</span> <b>Total</b></td>
    <td style="text-align:right;font-weight:bold;padding-bottom:0;">{format(cc_total_all, big.mark = ",")}</td>
    <td style="text-align:right;font-weight:bold;">{round(cc_total_prop * 100, 1)}%</td>
</tr></tbody></table>'))
 

 
pp <-  my_tooltips |>
  ungroup() |>
  mutate(max_ = max(cc_total_prop)) 


## Plot Top 3
p_top_3 <- cc_top |> 
  filter(publisher_fct %in% top[1:3]) |> 
  ggplot(aes(cr_year, prop,  fill = forcats::fct_rev(cc), group = forcats::fct_rev(cc))) +
    geom_area(
      #aes(fill = cc, group = cc),
      stat = "identity",
      color = "white",
      size = 0.3
    ) +
  geom_bar_interactive(data = filter(pp, publisher_fct %in% top[1:3]), 
                        inherit.aes = FALSE,
                        aes(cr_year, max_, tooltip = tooltip_group),
                        stat = "identity",
                        color = "transparent",
                        fill = "transparent",
                        alpha = 0.01,
                        width = 1,
                        position = position_dodge2()
                      ) + 
  facet_wrap(~publisher_fct, scales = "fixed", nrow = 1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L),
                       expand = expansion(mult = c(0, 0.05)),
                     breaks = scales::breaks_extended(3)) +
  scale_fill_manual("License spectrum",
                      values =  c(
                        `CC BY` = "#65BADA",
                        `CC BY-SA` = "#068E8C",
                        `CC BY-NC` = "#00A757",
                        `CC BY-NC-SA` = "#E5BA52",
                        `CC BY-ND` = "#D86F27",
                        `CC BY-NC-ND` = "#C82E6B"
                      ),
                      guide = guide_legend(nrow = 1)) +
    theme_minimal(base_family = "Source Sans Pro", base_size = 20) +
    labs(y = NULL, x = NULL) +
    #       title = "Open Access in Hybrid Journals",
    #       subtitle = "By Creative Commons license variant as provided by Crossref\n") +
    theme(panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          axis.text.x=element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.ontop = FALSE,
          legend.position="top", legend.justification = "right",
          legend.title=element_text(size = 14), 
    legend.text=element_text(size = 12)) 


p_other <-  cc_top |> 
  filter(publisher_fct %in% top[4:13]) |> 
  ggplot(aes(cr_year, prop,  fill = forcats::fct_rev(cc), group = forcats::fct_rev(cc))) +
    geom_area(
      #aes(fill = cc, group = cc),
      stat = "identity",
      color = "white",
      size = 0.3
    ) +
  geom_bar_interactive(data = filter(pp, publisher_fct %in% top[4:13]), 
                        inherit.aes = FALSE,
                        aes(cr_year, max_, tooltip = tooltip_group),
                        stat = "identity",
                        color = "transparent",
                        fill = "transparent",
                        alpha = 0.01,
                        width = 1,
                        position = position_dodge2()
                      ) + 
  facet_wrap(~publisher_fct, scales = "fixed", ncol = 5,
             labeller = label_wrap_gen(multi_line = TRUE)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L),
                       expand = expansion(mult = c(0, 0.05)),
                     breaks = scales::breaks_extended(3)) +
  scale_fill_manual("License spectrum",
                      values =  c(
                        `CC BY` = "#65BADA",
                        `CC BY-SA` = "#068E8C",
                        `CC BY-NC` = "#00A757",
                        `CC BY-NC-SA` = "#E5BA52",
                        `CC BY-ND` = "#D86F27",
                        `CC BY-NC-ND` = "#C82E6B"
                      )) +
    theme_minimal(base_family = "Source Sans Pro", base_size = 14) +
    labs(y = NULL, x = NULL) +
    #       title = "Open Access in Hybrid Journals",
    #       subtitle = "By Creative Commons license variant as provided by Crossref\n") +
    theme(panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          axis.text.x=element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.ontop = FALSE,
          legend.position="none")



# Merge into one plot

publisher_p <-  p_top_3 / p_other +
plot_layout(guides = 'keep')
```

```{r}
### DE
de_df <- jct_hybrid_jns |>
  distinct(jn_id = issn_l, esac_publisher) |>
  mutate(publisher_fct = forcats::fct_other(esac_publisher, keep = top)) |>
  mutate(publisher_fct = forcats::fct_relevel(publisher_fct, top, "Other")) |>
  inner_join(cc_openalex_inst_jn_ind, by = "jn_id") |>
  distinct() |>
  filter(country_code == "DE")

de_total <- de_df |>
    distinct(cr_year, jn_id, articles_total, publisher_fct) %>%
    group_by(cr_year, publisher_fct) %>%
    summarize(jn_all = sum(articles_total))

de_top <- de_df |>
    filter(!is.na(cc)) |>
  # Create Other category
    mutate(publisher_fct = forcats::fct_other(esac_publisher, keep = top)) |>
    mutate(publisher_fct = forcats::fct_relevel(publisher_fct, top, "Other")) |>
    distinct(cr_year, jn_id, articles_under_cc_variant, cc, publisher_fct) |>
    group_by(cr_year, cc, publisher_fct) |>
    summarize(cc_total = sum(articles_under_cc_variant)) |>
  # We also wanna include journals without OA article in a single year
    right_join(de_total, by = c("cr_year", "publisher_fct")) |>
    mutate(cr_year = factor(cr_year)) %>%
    mutate(prop = cc_total / jn_all) %>%
    mutate_if(is.numeric, ~replace(., is.na(.), 0)) |>
  ungroup() |>
   tidyr::complete(cc, nesting(cr_year, publisher_fct), fill = list(cc_total = 0, prop = 0))
  
  
# # validate
# sum(de_total$jn_all)
# de_cc %>% ungroup() %>% 
#   distinct(publisher_fct, cr_year, jn_all) %>%
#   pull(jn_all) %>%
#   sum()

# 
# de_top <- de_cc |>
#   ungroup() |>
#   mutate(publisher_fct = forcats::fct_other(esac_publisher, keep = top)) |>
#   mutate(publisher_fct = forcats::fct_relevel(publisher_fct, top, "Other")) |>
#   group_by(cr_year, publisher_fct, cc) |>
#   summarise(cc_total = sum(cc_total), jn_all = sum(jn_all)) |>
#   mutate(prop = cc_total / jn_all) |>
#   ungroup() |>
#   tidyr::complete(cc, nesting(cr_year, publisher_fct), fill = list(cc_total = 0, prop = 0))
```

```{r}
## tooltips 
total_by_year <- de_top |>
  group_by(cr_year, publisher_fct) |>
  summarise(cc_total_all = sum(cc_total),
              cc_total_prop = sum(prop))
  
 my_tooltips <-
   de_top |>
   filter(!is.na(cc)) |>
    mutate(colors = case_when(
        cc == "CC BY" ~ "#65BADA",
        cc == "CC BY-SA" ~ "#068E8C",
        cc == "CC BY-NC" ~ "#00A757",
        cc == "CC BY-NC-SA" ~ "#E5BA52",
        cc == "CC BY-ND" ~ "#D86F27",
        cc == "CC BY-NC-ND" ~ "#C82E6B")) |>
      mutate(tooltip = glue::glue('
<tr>
    <td style="text-align:left;padding-bottom:0"><span style="color:{colors}">■</span> {cc}<br></td>
    <td style="text-align:right;padding-bottom:0">{format(cc_total, big.mark = ",")}</td>
    <td style="text-align:right;">{round(prop * 100, 1)}%</td>
</tr>')) |>
      group_by(cr_year, publisher_fct) |>
      summarise(tooltip_group = paste(tooltip, collapse = "")) |>
      inner_join(total_by_year, by = c("cr_year", "publisher_fct")) |>
      mutate(tooltip_group = glue::glue('<h4><b>{publisher_fct}</b><br><span class="text-muted">Articles with Creative Commons license<br>in</span> <b>{cr_year}</b></h4><hr><table style="margin:8px 0 0;padding:0;width:100%">
  <colgroup>
       <col span="1" style="width: 50%;">
       <col span="1" style="width: 30%;">
       <col span="1" style="width: 20%;">
      </colgroup>
    <tbody>
    {tooltip_group}
 <tr style="padding-top:5px">
    <td style="text-align:left;padding-bottom:0;font-weight:bold;"><span style="color:transparent">■</span> <b>Total</b></td>
    <td style="text-align:right;font-weight:bold;padding-bottom:0;">{format(cc_total_all, big.mark = ",")}</td>
    <td style="text-align:right;font-weight:bold;">{round(cc_total_prop * 100, 1)}%</td>
</tr></tbody></table>'))
 

pp <-  my_tooltips |>
  ungroup() |>
  mutate(max_ = max(cc_total_prop)) 
```

```{r}
## Plot Top 3
p_de_top_3 <- de_top |> 
  filter(publisher_fct %in% top[1:3]) |> 
  ggplot(aes(cr_year, prop,  fill = forcats::fct_rev(cc), group = forcats::fct_rev(cc))) +
    geom_area(
      #aes(fill = cc, group = cc),
      stat = "identity",
      color = "white",
      size = 0.3
    ) +
   geom_bar_interactive(data = filter(pp, publisher_fct %in% top[1:3]), 
                          inherit.aes = FALSE,
                        aes(cr_year, max_, tooltip = tooltip_group),
                        stat = "identity",
                        color = "transparent",
                        fill = "transparent",
                        alpha = 0.01,
                        width = 1,
                        position = position_dodge2()
                      ) + 
  facet_wrap(~publisher_fct, scales = "fixed", nrow = 1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L),
                       expand = expansion(mult = c(0, 0.05)),
                     breaks = scales::breaks_extended(4)) +
  scale_fill_manual("License spectrum",
                      values =  c(
                        `CC BY` = "#65BADA",
                        `CC BY-SA` = "#068E8C",
                        `CC BY-NC` = "#00A757",
                        `CC BY-NC-SA` = "#E5BA52",
                        `CC BY-ND` = "#D86F27",
                        `CC BY-NC-ND` = "#C82E6B"
                      ),
                      guide = guide_legend(nrow = 1)) +
    theme_minimal(base_family = "Source Sans Pro", base_size = 20) +
    labs(y = NULL, x = NULL) +
    #       title = "Open Access in Hybrid Journals",
    #       subtitle = "By Creative Commons license variant as provided by Crossref\n") +
    theme(panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          axis.text.x=element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.ontop = FALSE,
          legend.position="top", legend.justification = "right",
          legend.title=element_text(size = 14), 
    legend.text=element_text(size = 12))


p_de_other <-  de_top |> 
  filter(publisher_fct %in% top[4:13]) |> 
  ggplot(aes(cr_year, prop,  fill = forcats::fct_rev(cc), group = forcats::fct_rev(cc))) +
    geom_area(
      #aes(fill = cc, group = cc),
      stat = "identity",
      color = "white",
      size = 0.3
    ) +
  geom_bar_interactive(data = filter(pp, publisher_fct %in% top[4:13]), 
                        inherit.aes = FALSE,
                        aes(cr_year, max_, tooltip = tooltip_group),
                        stat = "identity",
                        color = "transparent",
                        fill = "transparent",
                        alpha = 0.01,
                        width = 1,
                        position = position_dodge2()
                      ) + 
  facet_wrap(~publisher_fct, scales = "fixed", ncol = 5,
                                labeller = label_wrap_gen(multi_line = TRUE)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L),
                       expand = expansion(mult = c(0, 0.05)),
                     breaks = scales::breaks_extended(3)) +
  scale_fill_manual("License spectrum",
                      values =  c(
                        `CC BY` = "#65BADA",
                        `CC BY-SA` = "#068E8C",
                        `CC BY-NC` = "#00A757",
                        `CC BY-NC-SA` = "#E5BA52",
                        `CC BY-ND` = "#D86F27",
                        `CC BY-NC-ND` = "#C82E6B"
                      )) +
    theme_minimal(base_family = "Source Sans Pro", base_size = 14) +
    labs(y = NULL, x = NULL) +
    #       title = "Open Access in Hybrid Journals",
    #       subtitle = "By Creative Commons license variant as provided by Crossref\n") +
    theme(panel.grid.major.x = element_blank(),
          panel.grid.minor.x = element_blank(),
          axis.text.x=element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.ontop = FALSE,
          legend.position="none")



# Merge into one plot

publisher_p_de <-  p_de_top_3 / p_de_other +
plot_layout(guides = 'keep')

```

::: panel-tabset
## Global

```{r}
# Return SVG
girafe(
  ggobj = publisher_p,
  width_svg = 9,
  height_svg = 10 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

## Germany

```{r}
# Return SVG
girafe(
  ggobj = publisher_p_de,
  width_svg = 9,
  height_svg = 10 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```
:::

## Publishing Market

Hybrid journal portfolio analysis, showing publishing market shares in terms of total and Open Access article volume. Note that only hybrid journals included in transformative agreements are shown.

### Market Shares

Publisher market shares as measured by articles published between 2017 and 2022 in hybrid journals included in transformative agreements.

```{r}
## Global

## Total Article Volume
all_publisher_league <- all_top |>
  ungroup() |>
  group_by(publisher_fct) |>
  summarise(total_articles = sum(all_articles)) |>
  mutate(prop = total_articles / sum(total_articles)) |>
  mutate(cat = "Total Articles")

## CC Article Volume
cc_publisher_league <- cc_top |>
  ungroup() |>
  group_by(publisher_fct) |>
  summarise(total_articles = sum(cc_total)) |>
  mutate(prop = total_articles / sum(total_articles)) |>
  mutate(cat = "Open Access Articles with Creative Commons License")

pub_shares <- bind_rows(all_publisher_league, cc_publisher_league) |>
  mutate(type = case_when(
    publisher_fct == "Elsevier" ~ "Elsevier",
    publisher_fct == "Springer Nature" ~ "Springer Nature",
    publisher_fct == "Wiley" ~ "Wiley",
    publisher_fct %in% top_publisher[4:13] ~ "Top 4-13",
    publisher_fct == "Other" ~ "Other"
  ) ) |>
  mutate(type = forcats::fct_inorder(type)) |>
  mutate(cat = fct_rev(as.factor(cat))) |>
  # Tooltips
  mutate(my_tooltip = glue::glue('<p>{publisher_fct}</p>
                              <p><big>{format(total_articles, big.mark = ",")}</big> <span class="text-muted">Articles</span></p>
                              <p><big>{round(prop * 100, 1)}%</big><span class="text-muted"> <small>Market Share</small></span></p>'))

pub_shares_global <- ggplot(pub_shares, aes(
  x = "",
  y = prop,
  group = type,
  fill = type
)) +
  geom_bar_interactive(
    width = 1,
    stat = "identity",
    position = position_stack(reverse = TRUE),
    color = "white",
    aes(tooltip = my_tooltip)
  ) +
  coord_flip() +
  scale_fill_manual(
    "",
    values = c(
      "Elsevier" = "#e9711c",
      "Springer Nature" = "#486a7e",
      "Wiley" = "#068853",
      "Top 4-13" = "grey60",
      "Other" = "grey90"
    ),
    guide = guide_legend(reverse = FALSE,  nrow = 1)
  ) +
  facet_wrap(~ cat, ncol = 1) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(x = NULL, y = NULL) +
    theme_minimal(base_family = "Source Sans Pro", base_size = 14) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(strip.text.x = element_text(hjust = -0.01)) +
  theme(legend.position = "bottom",
        legend.justification = "center",
        legend.text = element_text(size = 10)) 
```

::: panel-tabset
## Global

```{r}
# Return SVG
girafe(
  ggobj = pub_shares_global,
  width_svg = 6,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

## Germany

```{r}
## Global

## Total Article Volume
all_publisher_league <- de_top |>
  ungroup() |>
  distinct(cr_year, publisher_fct, jn_all) |>
  group_by(publisher_fct) |>
  summarise(total_articles = sum(jn_all, na.rm =TRUE)) |>
  mutate(prop = total_articles / sum(total_articles)) |>
  mutate(cat = "Total Articles")

## CC Article Volume
cc_publisher_league <- de_top |>
  ungroup() |>
  group_by(publisher_fct) |>
  summarise(total_articles = sum(cc_total)) |>
  mutate(prop = total_articles / sum(total_articles)) |>
  mutate(cat = "Open Access Articles with Creative Commons License")

de_pub_shares <- bind_rows(all_publisher_league, cc_publisher_league) |>
  mutate(type = case_when(
    publisher_fct == "Elsevier" ~ "Elsevier",
    publisher_fct == "Springer Nature" ~ "Springer Nature",
    publisher_fct == "Wiley" ~ "Wiley",
    publisher_fct %in% top_publisher[4:13] ~ "Top 4-13",
    publisher_fct == "Other" ~ "Other"
  ) ) |>
  mutate(type = forcats::fct_inorder(type)) |>
  mutate(cat = fct_rev(as.factor(cat))) |>
  # Tooltips
  mutate(my_tooltip = glue::glue('<p>{publisher_fct}</p>
                              <p><big>{format(total_articles, big.mark = ",")}</big> <span class="text-muted">Articles</span></p>
                              <p><big>{round(prop * 100, 1)}%</big><span class="text-muted"> <small>Market Share</small></span></p>'))

pub_share_de <- ggplot(de_pub_shares, aes(
  x = "",
  y = prop,
  group = type,
  fill = type
)) +
  geom_bar_interactive(
    width = 1,
    stat = "identity",
    position = position_stack(reverse = TRUE),
    color = "white",
    aes(tooltip = my_tooltip)
  ) +
  coord_flip() +
  scale_fill_manual(
    "",
    values = c(
      "Elsevier" = "#e9711c",
      "Springer Nature" = "#486a7e",
      "Wiley" = "#068853",
      "Top 4-13" = "grey60",
      "Other" = "grey90"
    ),
    guide = guide_legend(reverse = FALSE,  nrow = 1)
  ) +
  facet_wrap(~ cat, ncol = 1) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1),
                     labels = scales::percent_format(accuracy = 5L)) +
  labs(x = NULL, y = NULL) +
  theme_minimal(base_family = "Source Sans Pro", base_size = 14) +
  theme(panel.grid.minor = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(panel.grid.major.y = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(strip.text.x = element_text(hjust = -0.01)) +
  theme(legend.position = "bottom",
        legend.justification = "center",
        legend.text = element_text(size = 10)) 
```

```{r}
# Return SVG
girafe(
  ggobj = pub_share_de,
  width_svg = 6,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```
:::

### Publisher League

This interactive table highlights the hybrid Open Access publisher output by year, sorted . It shows the number and proportion of Open Access articles provided under a Creative Commons license in hybrid journals included in transformative agreements. The table also illustrates the number of hybrid journals per portfolio, which published articles in the year, and the corresponding percentage of hybrid journals with at least one Open Access article. You can filter by publisher, publication year, and between a global and a country-specific view relative to lead author publications from Germany.

::: column-body-outset
{{< include _publisher_league.qmd >}}
:::

## Country View

This section shows how hybrid open access has been adopted in different parts of the world. The analysis is based on country-affiliations of lead authors. Lead authors are the first named authors of scholarly articles who have usually undertaken most of the research presented in the article, although author roles can vary across discipline. We used OpenAlex as data source to determine lead author affiliation.

### Open Access in Hybrid Journals by Country

Percentage of Open Access Articles with a Creative Commons license per country. Showing the Top 20 most productive countries in terms of articles published in hybrid journals included in transformative agreements between 2017 and 2022.

::: column-body-outset
{{< include _country_top20.qmd >}}
:::

### Country League

Publication volume in hybrid journals included in transformative agreements and Open Access share per country. You can search for specific countries, and filter by publisher and publication year.

{{< include _country_league_table.qmd >}}

## Open Metadata

Open metadata is a key requirement in many transformative agreements.

### License Metadata Gaps

Comparision of license metadata in Crossref with Unpaywall per year. Additionally to Crossref license information, Unpaywall also parses publisher websites to determine whether an article was published under an open content license.

{{< include _upw_cr.qmd >}}

## Journal Table
