---
title: "Hybrid Journals in Transformative Agreements"
subtitle: "How open are hybrid journals in transformative agreements? This open source dashboard highlights the Open Access uptake in hybrid journals included in transformative agreements as listed by the cOAlition S Journal Checker Tool. You can analyse progress made over time by open license, publisher and country. You can also monitor the availability of publisher-provided metadata in Crossref."
format:
  html:
    theme: default
    toc: true
    toc-location: right
execute:
  echo: false
  warnings: false
  message: false
  freeze: auto
sidebar: false
---

<!-- Required R packages -->

```{r setup}
#| echo: false
#| message: false
source("R/setup.R")
```

<!-- data preparation -->

```{r data prep}
#| echo: false
#| message: false
jn_ind_df <- hoaddata::jn_ind |>
dplyr::mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    ))) |>
  # Journal selection
  filter(issn_l %in% params$issn_l)

jn_aff_df <- hoaddata::jn_aff |>
dplyr::mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    ))) |>
  # Journal selection
  filter(issn_l %in% params$issn_l)
```


<!-- Teaser -->

The share of Open Access articles with a Creative Commons license in hybrid journals exposed by the [cOAlition S Journal Checker Tool](https://journalcheckertool.org/) is as follows:


```{r}
#| echo: false
#| message: false
#| warning: false
#| results: asis
source("R/teaser.R")
basic_stat(jn_ind_df = jn_ind_df, jn_aff_df = jn_aff_df)
```

::: {.callout-note collapse="true"}
## Expand to learn about how publications from Germany were counted?

Only journal articles from lead authors based in Germany were considered. A [lead author](https://en.wikipedia.org/wiki/Lead_author) is the first named author of a scholarly article who has usually undertaken most of the research presented in the article, although author roles can vary across discipline. We used [OpenAlex](https://openalex.org/) as data source to determine lead author affiliation.
:::

<!-- Creative Commons license prevalence-->

### Creative Commons licenses over time

Percentage of Open Access in hybrid journals included in transformative agreements by Creative Commons license types as provided by Crossref.

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/cc_over_year.R")
```


::: {.panel-tabset}

## Global

```{r, message=FALSE}
cc_global_plot <- plot_cc_variants_by_year(cc_ind_global(jn_ind_df = jn_ind_df))
# Return SVG
girafe(
  ggobj = cc_global_plot,
  width_svg = 9,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
# download
readr::write_csv(cc_ind_global(jn_ind_df = jn_ind_df), "cc_2017-22.csv")
```

<!-- <div style="text-align: right"><small>[Download data (csv)](cc_2017-22.csv)</small></div> -->

## Germany

```{r, message=FALSE}
cc_de_plot <- plot_cc_variants_by_year(cc_ind_de(jn_aff_df = jn_aff_df))
# Return SVG
girafe(
  ggobj = cc_de_plot,
  width_svg = 9,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
readr::write_csv(cc_ind_de(jn_aff_df = jn_aff_df), "cc_2017-22_de.csv")
```

<!--  <div style="text-align: right"><small>[Download data (csv)](cc_2017-22_de.csv)</small></div> -->

:::


### Publisher market

Hybrid journal portfolio analysis, showing publishing market shares in terms of total and Open Access article volume. Note that only hybrid journals included in transformative agreements are shown.

```{r}
#| echo: false
#| message: false
#| warning: false
# Data prep
source("R/data_prep.R")
my_df <- summarize_pubs(var_summary = c(cr_year, esac_publisher)) |>
  tidyr::complete(cr_year, esac_publisher, collection) |>
  mutate_if(is.numeric, ~ replace(., is.na(.), 0)) |>
  mutate(pub_col = ifelse(esac_publisher %in% params$publisher, "#0093C7", "#999999"))
```

::: {.panel-tabset}

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/pub_scatter.R")
```

## Global

```{r}
#| echo: false
#| message: false
#| warning: false
plot_scatterplot(my_df, collection = "global")
```
  
## Germany

```{r}
#| echo: false
#| message: false
#| warning: false
plot_scatterplot(my_df, collection = "de")
```

:::



## Country View

This section shows how hybrid open access has been adopted in different parts of the world. The analysis is based on country-affiliations of lead authors. Lead authors are the first named authors of scholarly articles who have usually undertaken most of the research presented in the article, although author roles can vary across discipline. We used OpenAlex as data source to determine lead author affiliation.

### Open Access in Hybrid Journals by Country

Percentage of Open Access Articles with a Creative Commons license per country. Showing the Top 20 most productive countries in terms of articles published in **`r params$publisher`** hybrid journals included in transformative agreements between 2017 and 2022.

::: column-body-outset
```{r}
#| echo: false
#| message: false
#| warning: false
source("R/country_top_20.R")

ggiraph::girafe(
  ggobj = country_multiple_plot,
  width_svg = 8,
  height_svg = 7 * 0.618,
  options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```
:::


### Country League

Publication volume in **`r params$publisher`** hybrid journals included in transformative agreements and Open Access share per country. You can search for specific countries, and filter by publisher and publication year.

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/country_league.R")
```

```{r}
htmltools::div(
  class = "agreement-tbl",
  htmltools::div(
    class = "filters",
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_country",
        "Countries",
        shared_oa_country_df,
        ~ country_name,
        multiple = TRUE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_country_year",
        "Publication Year",
        shared_oa_country_df,
        ~ cr_year,
        multiple = FALSE
      )
    )
  ),
  react_table_oa_country,
  htmltools::div(class = "agreement-footer", "
  Data sources: Journal Checker Tool, Crossref, OpenAlex")
)
```


```{js,echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_country_year").getElementsByClassName("selectized")[0].selectize.setValue("2021", false);
});
```

## Open Metadata

Open and comprehensive metadata is a key requirement in many transformative agreements. The following tables illustrate potential gaps in Crossref metadata relative to Open Access articles in hybrid journals included in transformative agreements.

### License Metadata Gaps

Comparision of license metadata in Crossref with Unpaywall per year. Additionally to Crossref license information, Unpaywall also parses publisher websites to determine whether an article was published under an open content license.

::: {.panel-tabset}

## Global 

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/cr_upw.R")
cr_upw_plot(cr_upw_data = hoaddata::cr_upw, params$issn_l, my_cat = "Global")
```

## Germany


```{r}
#| echo: false
#| message: false
#| warning: false
cr_upw_plot(cr_upw_data = hoaddata::cr_upw, params$issn_l, my_cat = "Germany")
```

:::

### Crossref Metadata Coverage

This interactive table shows the the proportion of Crossref metadata that is publicly available for Open Access articles in hybrid journals included in transformative agreements. Publishers can use Crossref to share links to full-texts for text-mining purposes,  persistent links to authors (ORCID) and funder information. They can also open up [abstracts](https://i4oa.org/) and [reference lists](https://i4oc.org/) through Crossref.


```{r}
#| echo: false
#| message: false
#| warning: false
source("R/open_md.R")
# Should be done in hoaddata  
md_tmp <- hoaddata::cr_md |> 
  tidyr::complete(cr_year, issn_l, cat) |>
  mutate_all(~ifelse(is.na(.), 0, .))

my_df <- shared_open_md_df(.data = md_tmp, issn_l = params$issn_l, publisher = params$publisher)

htmltools::div(
  class = "agreement-tbl",
  # filters,
  htmltools::div(
    class = "filters",
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_open_md_cat_input",
        "Global / Germany",
       my_df,
        ~ cat,
        multiple = FALSE
      )
    ),
  ),
  # table
  open_md_react(
    my_df
    ),
  # footer
  htmltools::div(
    class = "agreement-footer",
    paste(
      "Data sources: Journal Checker Tool, Crossref, OpenAlex. Last updated:",
      Sys.Date(),
      "."
    )
  )
)
```

```{js,echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_open_md_cat_input").getElementsByClassName("selectized")[0].selectize.setValue("Global", false);
});
```

## Journal Table

This table presents the publication volume and Open Access share by journal between 2017 and 2022, comparing global metrics with metrics just for Germany. Charts show the yearly Open Access share. You can search for journals or select a table header to sort by journal name or a metric.

::: column-body-outset


```{r}
#| echo: false
#| message: false
#| warning: false
my_df <- summarize_pubs(var_summary = c(cr_year, issn_l)) |>
  filter(issn_l %in% params$issn_l) |>
  tidyr::complete(cr_year, issn_l, collection) |>
  mutate_if(is.numeric, ~ replace(., is.na(.), 0)) 
```

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/journal_tbl.R")
htmltools::div(
  class = "agreement-tbl",
  journal_listing)
```

:::

```{css}
.my-tbl {
  margin: 0 auto;
  width: 575px;
}
.tbl-header {
  margin: 18px 0;
  font-size: 1.25em;
}
.filters {
  display: flex;
  flex-wrap: wrap;
  margin-top: 4px;
  margin-bottom: 24px;
  margin-left: auto;
  margin-right: auto;
}
.filter-input {
  margin-top: 4px;
  margin-left: 32px;
  flex: 1;
  max-width: 250px;
}
.filter-input label {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 13px;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}
.group-header {
  font-weight: 700;
  font-size: 14px;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}
.filter-input select,
.filter-input input[type="search"] {
  padding: 0 6px;
  height: 32px;
}
.filter-input input[type="search"] {
  /* Reset Bootstrap 3 styles */
  -webkit-appearance: searchfield;
}
.filter-input input[type="search"]::-webkit-search-cancel-button {
  /* Reset Bootstrap 3 styles */
  -webkit-appearance: searchfield-cancel-button;
}
.followers-tbl a {
  color: inherit;
}
.header {
  border-bottom: 2px solid #555;
  font-size: 14px;
  font-weight: bold;
  text-transform: uppercase;
}
.header:hover {
  background-color: #eee;
}
/* Highlight headers when sorting */
.header:hover,
.header[aria-sort="ascending"],
.header[aria-sort="descending"] {
  background-color: rgba(236, 236, 237, 1);
}
.agreement-footer {
  margin: 18px 0;
  font-size: 10px;
  }
  
.agreement-tbl {
  margin: 18px 0;
  font-size: 14px;
}
.bar-cell {
  display: flex;
  align-items: center;
}
.number {
  font-family: monospace;
  font-size: 14px;
  white-space: pre;
}
.label {
  font-size: 14px;
  white-space: pre;
}
.bar-chart {
  flex-grow: 1;
  margin-left: 6px;
  height: 14px;
}
.bar {
  height: 100%;
}
.border-left {
  border-left: 1px solid #b5b5b5;
}
.name {
  font-weight: 900;
}
```
