---
title: "How Open are Hybrid Journals in Transformative Agreements with Consortia in Germany?"
subtitle: "Open Access uptake in hybrid journals included in consortial transformative agreements in Germany. You can analyse progress made over time by open license, publisher and country. You can also monitor the availability of publisher-provided metadata in Crossref."
format:
  html:
    theme: default
    toc: true
    toc-location: right
execute:
  echo: false
  warnings: false
  message: false
sidebar: true
---

<!-- Required R packages -->

```{r setup}
#| echo: false
#| message: false
source("R/setup.R")
source("R/utils.R")
```

<!-- data preparation -->

```{r data prep}
#| echo: false
#| message: false
oam <- hoaddata::oam_hybrid_jns |>
      dplyr::distinct(issn_l, esac_publisher = vertrag) 

jn_ind_df <- hoaddata::jn_ind |>
  dplyr::inner_join(oam, by = "issn_l") |>
  dplyr::mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    ))) 

jn_aff_df <- hoaddata::jn_aff |>
  dplyr::inner_join(oam, by = "issn_l") |>
  dplyr::mutate(cr_year = as.character(cr_year)) |>
  dplyr::mutate(cc = factor(
    cc,
    # Order by permissiveness
    levels = c(
      "CC BY",
      "CC BY-SA",
      "CC BY-NC",
      "CC BY-NC-SA",
      "CC BY-ND",
      "CC BY-NC-ND"
    ))) 
```


<!-- Teaser -->

The share of Open Access articles with a Creative Commons license in hybrid journals exposed by the [German Open Access Monitor Team](https://doi.org/10.26165/JUELICH-DATA/VTQXLM) is as follows:


```{r teaser}
#| echo: false
#| message: false
#| warning: false
#| results: asis
source("R/teaser.R")
basic_stat(jn_ind_df = jn_ind_df, jn_aff_df = jn_aff_df)
```

<small>*Journal articles from lead authors based in Germany</small>

<!-- Creative Commons license prevalence-->

### Creative Commons licenses over time

Percentage of Open Access in hybrid journals included in transformative agreements by Creative Commons license types as provided by Crossref.

```{r cc_over_year_data}
#| echo: false
#| message: false
#| warning: false
source("R/cc_over_year.R")
```


::: {.panel-tabset}

## Global

```{r cc_over_year_global, message=FALSE}
cc_global_plot <- plot_cc_variants_by_year(cc_ind_global(jn_ind_df = jn_ind_df))
# Return SVG
girafe(
  ggobj = cc_global_plot,
  width_svg = 9,
  height_svg = 6 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```


## Germany<sup>*</sup>

```{r, message=FALSE}
cc_de_plot <- plot_cc_variants_by_year(cc_ind_de(jn_aff_df = jn_aff_df))
# Return SVG
girafe(
  ggobj = cc_de_plot,
  width_svg = 9,
  height_svg = 6 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

<small><sup>*</sup>Journal articles from lead authors based in Germany</small>

:::

### Creative Commons licenses over time by publisher

Percentage of Open Access in hybrid journals included in transformative agreements by Creative Commons license types and Top 13 publishers in terms of total articles published between 2017 and 2022.

```{r}
#| echo: false
#| message: false
#| warning: false
# Data prep
source("R/oam_data_prep.R")
```

::: panel-tabset

## Global

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/oam_publisher_cc.R")

# Return SVG
girafe(
  ggobj = top_13_plot("global") ,
  width_svg = 9,
  height_svg = 10 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

## Germany<sup>*</sup>

```{r}
#| echo: false
#| message: false
#| warning: false

# Return SVG
girafe(
  ggobj = top_13_plot("de"),
  width_svg = 9,
  height_svg = 10 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

<small><sup>*</sup>Journal articles from lead authors based in Germany</small>

:::

## Publishing market

### Publishing market over time

Hybrid journal publisher portfolio analysis, showing publishing market shares in terms of total and Open Access article volume. Note that only hybrid journals included in transformative agreements are shown.


```{r}
#| echo: false
#| message: false
#| warning: false
# Data prep
source("R/oam_data_prep.R")
my_df <- summarize_pubs(var_summary = c(cr_year, esac_publisher)) |>
  tidyr::complete(cr_year, esac_publisher, collection) |>
  mutate_if(is.numeric, ~ replace(., is.na(.), 0)) |>
  mutate(pub_col =  "#999999")
```

::: {.panel-tabset}

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/pub_scatter.R")
```

## Global

```{r}
#| echo: false
#| message: false
#| warning: false
plot_scatterplot(my_df, collection = "global")
```
  
## Germany<sup>*</sup>

```{r}
#| echo: false
#| message: false
#| warning: false
plot_scatterplot(my_df, collection = "de")
```

<small><sup>*</sup>Journal articles from lead authors based in Germany</small>

:::

### Market shares

Publisher market shares as measured by articles published between 2017 and 2022 in hybrid journals included in transformative agreements.

```{r}
#| echo: FALSE
source("R/oam_publisher_market_share.R")
```

::: panel-tabset

## Global

```{r}
# Return SVG
girafe(
  ggobj = plot_pub_shares(.cat = "global"),
  width_svg = 6,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

## Germany<sup>*</sup>

```{r}
# Return SVG
girafe(
  ggobj = plot_pub_shares(.cat = "de"),
  width_svg = 6,
  height_svg = 5 * 0.618,
 options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```

<small><sup>*</sup>Journal articles from lead authors based in Germany</small>

:::

### Publisher league: Hybrid Open Access output

This interactive table highlights the hybrid Open Access publisher output by year, sorted . It shows the number and proportion of Open Access articles provided under a Creative Commons license in hybrid journals included in transformative agreements. The table also illustrates the number of hybrid journals per portfolio, which published articles in the year, and the corresponding percentage of hybrid journals with at least one Open Access article. You can filter by publisher, publication year, and between a global and a country-specific view relative to lead author publications from Germany.

::: column-body-outset

```{r}
#| echo: false
#| message: false
source("R/publisher_league.R")
# Prepare data
table_df <- publisher_league_data_prep() |>
mutate(agreement_ = strsplit(esac_publisher, " \\(")) |>
  mutate(agreement = map_chr(agreement_, 1)) |>
  mutate(lead = map_chr(agreement_, 2)) |>
  mutate(lead = gsub(")", "", lead)) |>
  relocate(c(agreement, lead), .after = esac_publisher) |>
  select(-agreement_)

# Crosstalk init
shared_publisher_df <- SharedData$new(table_df)

# React table
g <- publisher_league_reactable(shared_publisher_df, .collection = "oam")

htmltools::div(
  class = "agreement-tbl",
  # filters,
  htmltools::div(class = "filters",
                 htmltools::div(
                   class = "filter-input",
                   filter_select(
                     "filter_cr_publisher",
                     "Agreement",
                     shared_publisher_df,
                     ~ esac_publisher,
                     multiple = TRUE
                   )
                 ),
                 htmltools::div(
                   class = "filter-input",
                   filter_select(
                     "filter_cr_publisher",
                     "CONSORTIUM LEAD",
                     shared_publisher_df,
                     ~ lead,
                     multiple = TRUE
                   )
                 ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_year",
        "Publication Year",
        shared_publisher_df,
        ~ cr_year,
        multiple = FALSE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_input",
        "Global / Germany",
        shared_publisher_df,
        ~ collection,
        multiple = FALSE
      )
    ),
  ),
  # table
  g,
  # footer
  htmltools::div(
    class = "agreement-footer",
    paste(
      "Data sources: Journal Checker Tool, Crossref, OpenAlex. Last updated:",
      Sys.Date(),
      "."
    )
  )
)
```

:::


```{js, echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_year").getElementsByClassName("selectized")[0].selectize.setValue("2022", false);
     document.getElementById("filter_input").getElementsByClassName("selectized")[0].selectize.setValue("Global", false);
});
```


## Country view

This section shows how hybrid open access has been adopted in different parts of the world. The analysis is based on country-affiliations of lead authors. Lead authors are the first named authors of scholarly articles who have usually undertaken most of the research presented in the article, although author roles can vary across discipline. We used OpenAlex as data source to determine lead author affiliation.

### Open Access in hybrid journals by country

Percentage of Open Access Articles with a Creative Commons license per country. Showing the Top 20 most productive countries in terms of articles published in hybrid journals included in transformative agreements between 2017 and 2022. The analysis is based on country-affiliations of lead authors.

::: column-body-outset
```{r}
#| echo: false
#| message: false
#| warning: false
source("R/country_top_20.R")

ggiraph::girafe(
  ggobj = country_multiple_plot,
  width_svg = 9,
  height_svg = 7 * 0.618,
  options = list(opts_tooltip(
    css="background-color:white;
;font-size:1.15em;padding:10px;border-radius:5px;box-shadow: 0 0 10px 0 rgba(0, 0, 0, 0.5)",
    opacity = .95)))
```
:::

### Country League

Publication volume in hybrid journals included in transformative agreements and Open Access share per country. You can search for specific countries, and filter by publisher and publication year. The analysis is based on country-affiliations of lead authors.

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/country_publisher_league.R")
```


```{r}
htmltools::div(
  class = "agreement-tbl",
  htmltools::div(
    class = "filters",
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_country",
        "Countries",
        shared_oa_country_df,
        ~ country_name,
        multiple = TRUE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_country_deal",
        "Publisher",
        shared_oa_country_df,
        ~ esac_publisher,
        multiple = FALSE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_country_year",
        "Publication Year",
        shared_oa_country_df,
        ~ cr_year,
        multiple = FALSE
      )
    )
  ),
  react_table_oa_country,
  htmltools::div(class = "agreement-footer", "
  Data sources: Journal Checker Tool, Crossref, OpenAlex")
)
```


```{js,echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_country_year").getElementsByClassName("selectized")[0].selectize.setValue("2022", false);
    document.getElementById("filter_country_deal").getElementsByClassName("selectized")[0].selectize.setValue("All", false);
});
```

## Open metadata

Open and comprehensive metadata is a key requirement in many transformative agreements. The following tables illustrate potential gaps in Crossref metadata relative to Open Access articles in hybrid journals included in transformative agreements.

### License metadata gaps

Comparison of open licence metadata in Crossref with Unpaywall per year. You can compare global metrics with metrics only for articles by lead authors based in Germany. In addition to Crossref licence information, Unpaywall also analyses publishers' websites to determine whether an article has been published under an open content licence. A positive gap indicates a licensing delay by Unpaywall, while a negative gap indicates that the publisher has not provided licensing metadata to Crossref.


```{r upw_cr_license_gaps_data_prep}
#| echo: false
#| message: false
#| warning: false
upw_cr_diff_year <- hoaddata::cr_upw |>
  dplyr::inner_join(oam, by = "issn_l") |>
  mutate(agreement_ = strsplit(esac_publisher, " \\(")) |>
  mutate(agreement = map_chr(agreement_, 1)) |>
  mutate(lead = map_chr(agreement_, 2)) |>
  mutate(lead = gsub(")", "", lead)) |>
  relocate(c(agreement, lead), .after = esac_publisher) |>
  select(-agreement_) |>
  mutate(esac_publisher = forcats::fct_relevel(forcats::as_factor(esac_publisher), publ_league)) |>
  group_by(cr_year, esac_publisher, cat, lead, agreement) |>
  summarise(
    article_total = sum(article_total),
    upw_hybrid_total = sum(upw_hybrid_total),
    cr_hybrid_total = sum(cr_hybrid_total)
  ) |>
  mutate(perc_upw = upw_hybrid_total / article_total,
         perc_cr = cr_hybrid_total / article_total) |>
  mutate(perc_diff = perc_cr - perc_upw) |>
  mutate(across(starts_with("perc_"), round, digits = 3)) |>
  select(-contains("total"),-article_total) |>
  relocate(perc_cr, .before = perc_upw)
```

```{r upw_cr_license_gaps_data_table}
source("R/cr_upw.R")

shared_upw_cr_diff_year <- upw_cr_diff_year |>
  arrange(esac_publisher) |>
  SharedData$new()
upw_cr_react_tbl <- upw_cr_react(shared_upw_cr_diff_year, "oam")
```

```{r}
htmltools::div(
  class = "agreement-tbl",
  # filters,
  htmltools::div(class = "filters",
                 htmltools::div(
                   class = "filter-input",
                   filter_select(
                     "filter_cr_publisher",
                     "Agreement",
                     shared_upw_cr_diff_year,
                     ~ esac_publisher,
                     multiple = TRUE
                   )
                 ),
                 htmltools::div(
                   class = "filter-input",
                   filter_select(
                     "filter_cr_publisher",
                     "CONSORTIUM LEAD",
                     shared_upw_cr_diff_year,
                     ~ lead,
                     multiple = TRUE
                   )
                 ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_cr_year",
        "Publication Year",
        shared_upw_cr_diff_year,
        ~ cr_year,
        multiple = FALSE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_cr_input",
        "Global / Germany",
        shared_upw_cr_diff_year,
        ~ cat,
        multiple = FALSE
      )
    ),
  ),
  # table
  upw_cr_react_tbl,
  # footer
  htmltools::div(
    class = "agreement-footer",
    paste(
      "Data sources: Journal Checker Tool, Crossref, OpenAlex. Last updated:",
      Sys.Date(),
      "."
    )
  )
)
```

```{js, echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_cr_year").getElementsByClassName("selectized")[0].selectize.setValue("2022", false);
     document.getElementById("filter_cr_input").getElementsByClassName("selectized")[0].selectize.setValue("Global", false);
});
```


### Crossref metadata coverage

This interactive table shows the the proportion of Crossref metadata that is publicly available for Open Access articles in hybrid journals included in transformative agreements. Publishers can use Crossref to share links to full-texts for text-mining purposes,  persistent links to authors (ORCID) and funder information. They can also open up [abstracts](https://i4oa.org/) and [reference lists](https://i4oc.org/) through Crossref.


```{r}
#| echo: false
#| message: false
#| warning: false
source("R/open_md.R")
# Should be done in hoaddata  
pub_md <-  oam |>
  inner_join(hoaddata::cr_md) |> 
  tidyr::complete(esac_publisher, cr_year, issn_l, cat) |>
  mutate(esac_publisher = forcats::fct_relevel(forcats::as_factor(esac_publisher), publ_league)) |> 
 mutate(across(where(is.numeric), replace_na, 0))

open_md_df <- shared_open_md_df(.data = pub_md, issn_l = pub_md$issn_l, publisher = pub_md$esac_publisher)

htmltools::div(
  class = "agreement-tbl",
  # filters,
  htmltools::div(
    class = "filters",
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_open_md_cat_publisher",
        "Agreement",
        open_md_df,
        ~ esac_publisher,
        multiple = TRUE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_open_md_input",
        "Metadata",
        open_md_df,
        ~ name,
        multiple = TRUE
      )
    ),
    htmltools::div(
      class = "filter-input",
      filter_select(
        "filter_open_md_cat_input",
        "Global / Germany",
        open_md_df,
        ~ cat,
        multiple = FALSE
      )
    ),
  ),
  # table
  open_md_react(
    open_md_df
    ),
  # footer
  htmltools::div(
    class = "agreement-footer",
    paste(
      "Data sources: Journal Checker Tool, Crossref, OpenAlex. Last updated:",
      Sys.Date(),
      "."
    )
  )
)
```

```{js,echo = FALSE}
 /* https://stackoverflow.com/a/66216595 */
$(document).ready(function() {
    document.getElementById("filter_open_md_cat_input").getElementsByClassName("selectized")[0].selectize.setValue("Global", false);
});
```

## Journal table

This table presents the publication volume and Open Access share by journal between 2017 and 2022, comparing global metrics with metrics only for articles by lead authors based in Germany. Charts show the yearly Open Access share. You can search for journals or select a table header to sort by journal name or a metric.

::: column-body-outset


```{r}
#| echo: false
#| message: false
#| warning: false
my_df <- summarize_pubs(var_summary = c(cr_year, issn_l)) |>
  tidyr::complete(cr_year, issn_l, collection) |>
  mutate_if(is.numeric, ~ replace(., is.na(.), 0)) 
```

```{r}
#| echo: false
#| message: false
#| warning: false
source("R/journal_tbl.R")
htmltools::div(
  class = "agreement-tbl",
  journal_listing)
```

:::

```{css}
.my-tbl {
  margin: 0 auto;
  width: 575px;
}
.tbl-header {
  margin: 18px 0;
  font-size: 1.25em;
}
.filters {
  display: flex;
  flex-wrap: wrap;
  margin-top: 4px;
  margin-bottom: 24px;
  margin-left: auto;
  margin-right: auto;
}
.filter-input {
  margin-top: 4px;
  margin-left: 32px;
  flex: 1;
  max-width: 250px;
}
.filter-input label {
  color: hsl(0, 0%, 45%);
  font-weight: 700;
  font-size: 13px;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}
.group-header {
  font-weight: 700;
  font-size: 14px;
  letter-spacing: 0.4px;
  text-transform: uppercase;
}
.filter-input select,
.filter-input input[type="search"] {
  padding: 0 6px;
  height: 32px;
}
.filter-input input[type="search"] {
  /* Reset Bootstrap 3 styles */
  -webkit-appearance: searchfield;
}
.filter-input input[type="search"]::-webkit-search-cancel-button {
  /* Reset Bootstrap 3 styles */
  -webkit-appearance: searchfield-cancel-button;
}
.followers-tbl a {
  color: inherit;
}
.header {
  border-bottom: 2px solid #555;
  font-size: 14px;
  font-weight: bold;
  text-transform: uppercase;
}
.header:hover {
  background-color: #eee;
}
/* Highlight headers when sorting */
.header:hover,
.header[aria-sort="ascending"],
.header[aria-sort="descending"] {
  background-color: rgba(236, 236, 237, 1);
}
.agreement-footer {
  margin: 18px 0;
  font-size: 10px;
  }
  
.agreement-tbl {
  margin: 18px 0;
  font-size: 14px;
}
.bar-cell {
  display: flex;
  align-items: center;
}
.number {
  font-family: monospace;
  font-size: 14px;
  white-space: pre;
}
.label {
  font-size: 14px;
  white-space: pre;
}
.bar-chart {
  flex-grow: 1;
  margin-left: 6px;
  height: 14px;
}
.bar {
  height: 100%;
}
.border-left {
  border-left: 2px solid #b5b5b5;
}
.name {
  font-weight: 900;
}
```

